### 2023-09-22 sections/languages.tex
LPPL v1.3c
Update languages.tex

\cvskill
{Languages} 
{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), French}

\cvskill
{} 
{(elemental reading skills)} \\

>>>>

\cvskill
{Languages} 
{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), Italian}

\cvskill
{} 
{(elemental reading skills), French (elemental reading skills)} \\
